Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
denote function composition. This provides an example that a well-behaved
quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
quantum IVPMs happen when mapping to other kind of intervals. For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation} 
\iota_1(x)=\cases{ 
\necess & if $x=1$ ;\\ 
\imposs & if $x=0$ ;\\ 
\unknown & otherwise. 
}\label{eq:homomorphism-1} \end{equation}
, and we still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.

>>>>

First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
denote function composition. This provides an example that a well-behaved
quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
quantum IVPMs happen when mapping to other kind of intervals. For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation} 
\iota_1(x)=\cases{ 
\necess & if $x=1$ ;\\ 
\imposs & if $x=0$ ;\\ 
\unknown & otherwise. 
}\label{eq:homomorphism-1} \end{equation}
We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.

Although the quantum IVPM listed above are all well-behaved, there
are some quantum IVPMs far from the Born rule. Consider $\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
defined by $\bar{\mu}(P)=\unknown$ for every projection~$P$. Since
every quantum probability measure is in the core of $\bar{\mu}$,
this measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question.
